Digital Analysis of Paintings

### 2014-04-30 paper.tex
Blah...

>>>>

A lot of analysis can be gained from passing filters over an image and
considering the colours used. However, a lot of these depend on some way of
statistically analysing the results. This section will look at some of the
research that considers some of the more statistical elements to provide
analysis.

Whilst gaining results of analysis techniques, it is also important to be able
to interpret them digitally for some form of use; determining whether a
painting is authentic or not, or dating an artist's work within a set of their
known work.
